Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-03-27 thesis/latex8.tex
sdsadf

\author{John Burchell \qquad William Granli \\
		john.a.burchell@gmail.com \qquad william.granli@gmail.com \\
		Computer Science and Engineering  \\
		University of Gothenburg }

@@

>>>>

\author{John Burchell \qquad William Granli  \qquad Imed Hammouda \\
		john.a.burchell@gmail.com \qquad william.granli@gmail.com \qquad hammouda@chalmers.se \\
		Computer Science and Engineering  \\
		University of Gothenburg }

@@

\section{Timeplan}
Table 1 is an initial timeline of milestones in our study. The dates are approximate and we aim to finish ahead of schedule.

\begin{table}
	\centering
	\begin{tabular}[!HT]{| l | l | l |}
	\hline
	\textbf{\#} & \textbf{Description} & \textbf{Deadline} \\
	\hline
	1 & Literature Review & 5 April \\
	\hline
	2 & Data Collection (Archival) & 12 April \\
	\hline
	3 & Data Analysis (Archival) & 19 April \\
	\hline
	4 & Data Collection (Interview) & 26 April \\
	\hline
	5 & Data Analysis (Everything) & 11 May \\
	\hline
	6 & Report Results & 25 May \\
	\hline
\end{tabular}
	\caption{Timeplan}
\end{table}
